### 2020-06-01 paper.tex
Add Assumptions Subsection

Insert assumptions here

>>>>

The proposed algorithm is software simulated using a program written in Java. This program simulates a $10*10$ grid on which cells are placed randomly. Cells are assumed to be identical. Each cell occupies a single unit of space on the grid and each cell has the same number of input and output ports which are $1$ and $2$ respectively. Cells input and output interconnections are mapped randomly, too, but under the condition that every cell is connected to only $2$ other cells.
